### 2016-11-17 CV/Brian Goldman CV.tex
Job at CSU is a postdoc for now
Updated CV to say that I've started the CSU Job
Updated CV

\documentclass[a4paper,11pt]{article}
\usepackage{cv}
\usepackage{verbatim}
\setlist[itemize,enumerate]{noitemsep,nolistsep}
\name{Brian W. Goldman}
\info{Address: & Department of Computer Science \& Engineering, Michigan State University, East Lansing, Michigan.\\
      Phone: & 314-313-1281\\
      Email: & brianwgoldman@acm.org\\
      Website: & \url{http://brianwgoldman.github.io/}}

@@

\addtocategory{journals}{goldman:2015:cgpanalysis,goldman:2015:fastp3,white:2013:bgpb,lehmann:2013:mimics}
%At MSU
\addtocategory{papers}{goldman:2014:p3,goldman:2015:GBO}
%CGP
\addtocategory{papers}{goldman:2013:ordering,goldman:2013:cgpwaste}
%With Tauritz
\addtocategory{papers}{goldman:2012:ltga,goldman:2011:scx,kamrath:2013:supportivescx,goldman:2012:supportive}

\addtocategory{posters}{goldman:2011:dynamic-parameters}

\addtocategory{curpapers}{goldman:2016:hyperplane,goldman:2016:p3hiff,whitley:2016:mkl}
%\ref{sumpapers} A list of these appears on pages \pageref{papersstart}--\pageref{papersend}.

@@

\section{Education}
\begin{itemize}
\item 2015 Doctor of Philosophy in Computer Science \& Engineering, Michigan State University
\begin{itemize}
  \item Dissertation Advisor:  Dr. William F. Punch%, GPA: 4.0/4.0
  \item Dissertation: Out of the Box Optimization using the Parameter-less Population Pyramid
\end{itemize}
\item 2012 Master of Science in Computer Science, Missouri University of Science and Technology
\begin{itemize}
  \item Thesis Advisor:  Dr. Daniel R. Tauritz%, GPA: 4.0/4.0
  \item Thesis: Robust Evolutionary Algorithms
\end{itemize}
\item 2010 Bachelor of Science in Computer Science, Missouri University of Science and Technology
%\begin{itemize}
%  \item Minor in Mathematics, GPA: 3.84/4.0 in major, 3.81/4.0 overall
%\end{itemize}
\end{itemize}
\section{Academic Positions}
\begin{itemize}
\item Research Assistant Professor, Colorado State University. Starting Spring 2016.
\item Postdoc, Hintze Lab, Michigan State University. Fall 2015.
\item Advanced Computing Solutions Program, Los Alamos National Laboratories. Summer 2012.
\item Center for Cyber Defenders, Sandia National Laboratories. Summer 2011.
\end{itemize}

@@

\section{Awards}
\begin{itemize}
\item     Runner-up, Best Paper - Genetic Algorithms Track for GECCO 2015 ``Gray Box Optimization using the Parameter-less Population Pyramid''
\item     Best Paper - Genetic Algorithms Track for GECCO 2014 ``Parameter-less Population Pyramid''
\item     Voted 2012 Leader of the Year, Missouri S\&T Computer Science Department
\item     Google AI challenge, ranked 25$^{th}$ out of 4619 world wide, 6$^{th}$ in USA, 2010
\item     Missouri S\&T Human versus Computer chess tournament, two first place AIs, 2009 and 2011
\end{itemize}

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage{cv}
\usepackage{verbatim}
\setlist[itemize,enumerate]{noitemsep,nolistsep}
\name{Brian W. Goldman}
\info{Address: & Google, Building 2600, Boulder, Colorado.\\
      Phone: & 314-313-1281\\
      Email: & brianwgoldman@acm.org\\
      Website: & \url{http://brianwgoldman.github.io/}}

@@

\addtocategory{journals}{whitley:2016:mkl,goldman:2015:cgpanalysis,goldman:2015:fastp3,white:2013:bgpb,lehmann:2013:mimics}
%At MSU
\addtocategory{papers}{goldman:2014:p3,goldman:2015:GBO,goldman:2016:hyperplane,goldman:2016:p3hiff}
%CGP
\addtocategory{papers}{goldman:2013:ordering,goldman:2013:cgpwaste}
%With Tauritz
\addtocategory{papers}{goldman:2012:ltga,goldman:2011:scx,kamrath:2013:supportivescx,goldman:2012:supportive}

\addtocategory{posters}{goldman:2011:dynamic-parameters,chen:2016:sat}

%\addtocategory{curpapers}{,}
%\ref{sumpapers} A list of these appears on pages \pageref{papersstart}--\pageref{papersend}.

@@

\section{Education}
\begin{itemize}
\item 2015 Doctor of Philosophy in Computer Science \& Engineering, Michigan State University
\begin{itemize}
  \item Dissertation Advisor:  Dr. William F. Punch%, GPA: 4.0/4.0
  \item Dissertation: Out of the Box Optimization using the Parameter-less Population Pyramid
\end{itemize}
\item 2012 Master of Science in Computer Science, Missouri University of Science and Technology
\begin{itemize}
  \item Thesis Advisor:  Dr. Daniel R. Tauritz%, GPA: 4.0/4.0
  \item Thesis: Robust Evolutionary Algorithms
\end{itemize}
\item 2010 Bachelor of Science in Computer Science, Missouri University of Science and Technology
%\begin{itemize}
%  \item Minor in Mathematics, GPA: 3.84/4.0 in major, 3.81/4.0 overall
%\end{itemize}
\end{itemize}
\section{Employment}
\begin{itemize}
\item Google Software Engineer. Fall 2016.
\item Postdoc, Whitley Lab, Colorado State University. Spring 2016.
\item Postdoc, Hintze Lab, Michigan State University. Fall 2015.
\item Advanced Computing Solutions Program, Los Alamos National Laboratories. Summer 2012.
\item Center for Cyber Defenders, Sandia National Laboratories. Summer 2011.
\end{itemize}

@@

\section{Awards}
\begin{itemize}
\item     Nominated, Best Paper - European Conference on Evolutionary Computation in Combinatorial Optimisation 2016 ``Hyperplane Elimination for Quickly Enumerating Local Optima''
\item     Runner-up, Best Paper - Genetic Algorithms Track for GECCO 2015 ``Gray Box Optimization using the Parameter-less Population Pyramid''
\item     Best Paper - Genetic Algorithms Track for GECCO 2014 ``Parameter-less Population Pyramid''
\item     Voted 2012 Leader of the Year, Missouri S\&T Computer Science Department
\item     Google AI challenge, ranked 25$^{th}$ out of 4619 world wide, 6$^{th}$ in USA, 2010
\item     Missouri S\&T Human versus Computer chess tournament, two first place AIs, 2009 and 2011
\end{itemize}
